---
title: "Final Project"
author: "Katie Briggs"
date: "5/28/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Library
```{r library, echo=FALSE}
library(ggplot2)
library(tidyverse)
library(dbplyr)
library(infer)
library(ggpubr)
library(ppcor)
library(boot)
library(car)
library(QuantPsyc)
library(ggExtra)
library(psych)
library(readxl)
library(devtools)
library(foreign)
library(caret)
library(lattice)
library(class)
library(gmodels)
library(pastecs)
```







## Include Histograms to determine Normality
# Here is was determined that the adult counts were skewed to the left.

```{r hist adult count, echo=TRUE}
ggplot(GroupTable, aes(x = Adult_Count)) + geom_histogram(aes(y = ..density..), 
binwidth = 5, size = 5, col = "blue") + geom_density(alpha = .2, fill = "#FF6666")
```
# Here is was determined that the hatchery production are skewed a little to the left and not unimodal.

```{r Hatch Hist, echo=TRUE}
ggplot(Hatchery, aes(x = Actual_Adult_Hatchery_Produced)) + geom_histogram(aes(y = ..density..), 
binwidth = 5, size = 5, col = "blue") + geom_density(alpha = .2, fill = "#FF6666")
```

# Abundanced Quantity is flat across the board, meaning that adundance of wild salmon is not normally distributed. 
```{r hist AQ, echo=TRUE}
ggplot(GroupTable, aes(x = AbundanceQuantity)) + geom_histogram(aes(y = ..density..), 
binwidth = 5, size = 5, col = "blue") + geom_density(alpha = .2, fill = "#FF6666")
```

# The species returning are Chinook, Coho and Chum Salmon.  

```{r Species, echo=TRUE}
ggplot(GroupTable, aes(x = Species)) + geom_histogram(stat = "count")

```

# QQplots
```{r QQ AdultCount, echo=TRUE}
ggplot(GroupTable, aes(sample = Adult_Count )) + stat_qq(col = "blue")
qqnorm(GroupTable$Adult_Count)
qqline(GroupTable$Adult_Count)
```

```{r qq aq, echo=TRUE}
ggplot(GroupTable, aes(sample = AbundanceQuantity)) + stat_qq(col = "blue")
qqnorm(GroupTable$AbundanceQuantity)
qqline(GroupTable$AbundanceQuantity)
```

# descriptive statistics
```{r stat, echo=TRUE}
stat.desc(GroupTable$Adult_Count, basic=TRUE, desc=TRUE, norm=FALSE, p=0.95)
stat.desc(GroupTable$AbundanceQuantity, basic=TRUE, desc=TRUE, norm=FALSE, p=0.95)
```

```{r Regression, echo=TRUE}
# Regression
ggplot(GroupTable, aes(x = Species, y = Adult_Count, color = Species)) +
  geom_jitter()
  
ggplot(GroupTable, aes(x = Species,y = AbundanceQuantity)) + geom_point() + 
  labs(x = "Species", y = "Abundance", title = 'Final Project') + 
  geom_smooth(method = 'lm', se = FALSE,)

ggplot(GroupTable, aes(x = Species,y = Adult_Count)) + geom_point() + 
  labs(x = "Species", y = "Adult Counts", title = 'Final Project') + 
  geom_smooth(method = 'lm', se = FALSE,)
```
# Linear Regression

```{r LR, echo=TRUE}
ggplot(Hatch_subset, aes(x = AdultReturnsTotal,y = Actual_Adult_Hatchery_Produced )) + geom_point() + 
  labs(x = "Returns", y = "Produced", title = 'Final Project') + 
  geom_smooth(method = 'lm', se = FALSE,)
```

```{r lm, echo=TRUE}
lm(formula = Actual_Adult_Hatchery_Produced ~ AdultReturnsTotal, data = Hatch_subset)
```


```{r test, echo=TRUE}
shapiro.test(Hatch_subset$Actual_Adult_Hatchery_Produced)
shapiro.test(Hatch_subset$AdultReturnsTotal)
```

```{r cortest, echo=TRUE}
cor.test(Hatch_subset$Actual_Adult_Hatchery_Produced,Hatch_subset$AdultReturnsTotal,
         method = "pearson",conf.level = .99)
```

